\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ulem}
\usepackage{xifthen}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \if\relax\detokenize{#5}\relax
        % Do nothing if #5 is empty
      \else
        \multicolumn{2}{@{}l}{\textit{\small#5}} \\
      \fi
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Matilde Silva} \\ \vspace{10pt}
    \small \href{https://matilde-silva-21.github.io/}{\uline{Personal Website}} $|$ \href{mailto:x@x.com}{\uline{matilde.m.silva.21@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/matilde-m-silva/}{\uline{linkedin.com/in/matilde-m-silva/}} $|$
    \href{https://github.com/matilde-silva-21}{\uline{github.com/matilde-silva-21}}
\end{center}


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Golang, Javascript, Python, Rust, SQL, Swift, Typescript} \\
     \textbf{Frameworks}{: Flutter, Laravel, NodeJS, ReactJS, SvelteKit, SwiftUI} \\
     \textbf{Developer Tools}{: Docker, Figma, Git, Jenkins, Jupyter Notebook, Microsoft Azure, Visual Studio Code, XCode}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {\href{https://sigarra.up.pt/feup/en/WEB_PAGE.INICIAL}{University of Porto}}{Sep. 2023 - Jul. 2025}
      {Master’s in Informatics and Computing Engineering}{Oporto, Portugal}
      {Current Grade: 16/20}
    \resumeSubheading
      {\href{https://informatics.tuwien.ac.at/}{Technische Universität Wien}}{Sep. 2024 - Feb. 2025}
      {Exchange Program Erasmus+}{Vienna, Austria}
      {}
    \resumeSubheading
      {\href{https://sigarra.up.pt/feup/en/WEB_PAGE.INICIAL}{University of Porto}}{Sep. 2020 - Jul. 2023}
      {Bachelor’s in Informatics and Computing Engineering}{Oporto, Portugal}
      {Final Grade: 15/20}
	\resumeSubheading
      {\href{https://www.cambridgeenglish.org/}{Cambridge Assessment}}{Nov. 2019}
      {Certificate of Proficiency in English - Council of Europe Level C2}{Oporto, Portugal}
      {Final Grade: 218/230}
  \resumeSubHeadingListEnd
\leavevmode \\ % Extra Line for space

%-----------EXPERIENCE-----------
%---Multiple Positions Heading---
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {iOS Internship}{Jul. 2024 - Aug. 2024}
        {\href{https://www.sky.com/}{Sky Portugal}}{Aveiro, Portugal}
        {}
        \resumeItemListStart
            \resumeItem{Selected as one of 900+ candidates nationwide for a 2-month summer internship for recent graduates based on soft skills and character traits}
            \resumeItem{Developed, implemented and tested in-app toast notifications using Swift and SwiftUI}
        \resumeItemListEnd

    \resumeSubheading
      {Intelligent Transport Systems Internship}{Feb. 2023 - Jul. 2023}
      {\href{https://www.armisgroup.com/intelligent-transport-systems/}{Armis Intelligent Transport Systems}}{Oporto, Portugal}
      {}
      \resumeItemListStart
        \resumeItem{Selected as one of 50+ candidates for a 6-month curricular internship based on academic success and skill potential}
        \resumeItem{Engineered a Machine Learning model to determine Traffic Status based on traffic data}
        \resumeItem{Deployed REST API, with Azure Cloud Services, to communicate with the server running the ML model}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\leavevmode \\ % Extra Line for space

%-----------Extracurriculars-----------
\section{Extracurriculars}
    \resumeSubHeadingListStart
      \resumeProjectHeading
                {\textbf{\href{https://ncgm.fe.up.pt/}{Computer Graphics and Multimedia Nucleus}}}{Sep. 2023 - Present}
          \resumeItemListStart
            \resumeItem{Participated in the organization of different game and media related events that brought together 60+ attendees}
			\resumeItem{Worked on the Entrepreneurial Relations department for the National Informatics Student Meetup (ENEI 2025) that brought together 700+ attendees}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://formulastudent.fe.up.pt/en/}{Formula Student Driverless FEUP}}}{May 2023 - Sep. 2023}
          \resumeItemListStart
            \resumeItem{Researched and developed technologies for autonomous driving systems}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\leavevmode \\ % Extra Line for space

%-------------------------------------------


%-----------------Projects------------------
\section{Projects}
\resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/matilde-silva-21/grs_project}{NetKing}} $|$ \emph{Typescript, Rust, Docker, Tauri}}{Feb. 2024 - Jul. 2024}
          \resumeItemListStart
            \resumeItem{Created a network management system to facilitate visualization and virtualization of networks with a partner}
            \resumeItem{Employed Docker containers to host different services, such as Nginx servers and a built from scratch DNS server}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/matilde-silva-21/SDLE_project}{List Llama}} $|$ \emph{Golang, ReactJS, RabbitMQ}}{Sep. 2023 - Jan. 2024}
          \resumeItemListStart
            \resumeItem{Developed a concurrent shopping list application based on \href{https://crdt.tech/}{Conflict-Free Replicated Data Types (CRDTs)}}
            \resumeItem{Architected a load-balancing service with an orchestrator to handle client requests to servers}
            \resumeItem{Implemented a shopping list sharing feature through the use of URLs}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\leavevmode \\ % Extra Line for space    
%-------------------------------------------
\end{document}
